---
title: "STAT 443 Spring 2024 Final Project Supplementary Material2"
author: "Scenario 3&4"
date: "UW ID: 20885166, Daolin(Chase) An"
output: 
    pdf_document:
      toc: true
      latex_engine: xelatex
      number_sections: yes
---

# Preliminary
```{r Pre, message=FALSE, warning=FALSE}
rm(list=ls())
set.seed("20885166")
library(forecast)
## Scenario 3&4 data
data.car <- read.csv("car.txt")
data.gas <- read.csv("gas.txt")
data.beer <- read.csv("beer.txt")
data.steel <- read.csv("steel.txt")
data.electricity <- read.csv("electricity.txt")
data.temperature <- read.csv("temperature.txt")
```

# Scenario3

## Original data Analysis
```{r}
data.beer.beforeNA <- data.beer$Value[1:200]
data.beer.afterNA <- data.beer$Value[231:435]
exog <- data.temperature$Value[147:581]## To match the length
```

### acf and pacf before NA
```{r fig.height=4}
ts.plot(data.beer.beforeNA)
acf(data.beer.beforeNA)
pacf(data.beer.beforeNA)
```

### acf and pacf after NA
```{r fig.height=4}
ts.plot(data.beer.afterNA)
acf(data.beer.afterNA)
pacf(data.beer.afterNA)
```

## Difference data
```{r}
data.beer.diff <- diff(data.beer$Value, lag = 12)
data.beer.diff.beforeNA <- data.beer.diff[1:188]
data.beer.diff.afterNA <- data.beer.diff[231:423]
```

### acf and pacf of differenced data before NA
```{r fig.height=4}
acf(data.beer.diff.beforeNA, 40)
pacf(data.beer.diff.beforeNA, 40)
```

### acf and pacf of differenced data after NA
```{r fig.height=4}
acf(data.beer.diff.afterNA, 40)
pacf(data.beer.diff.afterNA, 40)
```

## Try some orders
```{r Try some orders, cache=TRUE}
beer.fit1 <- astsa::sarima(log(data.beer$Value), 10, 1, 0, 4, 1, 3, 12, xreg = exog)
```


```{r sarima model, cache=TRUE}
beer.fit <- arima(log(data.beer$Value), order = c(10, 1, 0), 
                  seasonal = list(order=c(4, 1, 3), period = 12), xreg = exog)
```

## Kalman Smoothing
```{r}
data.beer.imputed <- data.beer
smoothResult <- KalmanSmooth(y = data.beer$Value, mod = beer.fit$model)
```

### Imputed Values on original times series
```{r}
smoothVal <- smoothResult$smooth
smoothState <- smoothVal[, 59]
imputedVal <- smoothState[202:231]
data.beer.imputed$Value[201:230] <- imputedVal
ts.plot(data.beer.imputed$Value)
```

### Confidence intervals for imputed values
```{r}
## Assume normal
smoothVar <- smoothResult$var[, 59, 59]
smoothSE <- sqrt(smoothVar[202:231])
Ci.upper <- imputedVal + 1.96 * smoothSE
CI.lower <- imputedVal - 1.96 * smoothSE
```

# Scenario 4

## Check if there is need to try different orders
```{r}
# beer.imputed.fit <- astsa::sarima(log(data.beer.imputed$Value), 10, 1, 0, 4, 1, 3, 12, xreg = exog)
```

It seems that picking different orders will not improve the model, so I will 
use the original ARIMAX model to make predictions.

## Descriptive Statistics
```{r beer Descriptive}
beer.mean <- mean(data.beer$Value, na.rm = TRUE); beer.mean
beer.var <- var(data.beer$Value, na.rm = TRUE); beer.var
beer.max_min <- range(data.beer$Value, na.rm = TRUE); beer.max_min
```


## Forecast 24 steps ahead
```{r}
beer.pred <- predict(beer.fit, n.ahead = 24, newxreg = mean(data.temperature$Value))
```

### Prediction interval
```{r}
beer.pred.val <- beer.pred$pred
beer.pred.se <- beer.pred$se
PI.lower <- exp(beer.pred.val - 1.96 * beer.pred.se)
PI.lower <- exp(beer.pred.val + 1.96 * beer.pred.se)
```


